---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
## use a token from our development account
## special care with path because wd is docs/ during pkgdown::build_site()
token_path <- rprojroot::find_package_root_file("tidyverse-noncaching-token.rds")
googledrive::drive_auth(token_path)
```

# googledrive

[![Build Status](https://travis-ci.org/tidyverse/googledrive.svg?branch=master)](https://travis-ci.org/tidyverse/googledrive)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidyverse/googledrive?branch=master&svg=true)](https://ci.appveyor.com/project/tidyverse/googledrive)[![Coverage Status](https://img.shields.io/codecov/c/github/tidyverse/googledrive/master.svg)](https://codecov.io/github/tidyverse/googledrive?branch=master) 

## Overview

googledrive allows you to interact with files on Google Drive from R.

## Installation

googledrive will soon be submitted to CRAN, but for now, install it from GitHub:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("tidyverse/googledrive")
```

## Usage

### Load googledrive

```{r}
library("googledrive")
```

```{r data-setup, include = FALSE}
CLEAN <- SETUP <- FALSE
if (isTRUE(CLEAN)) {
  del <- drive_rm(
    c("README-mirrors.csv", "~/abc", "boring-text.txt"),
    verbose = FALSE
  )
}
if (isTRUE(SETUP)) {
  drive_mkdir("abc")
  drive_mkdir("abc/def")
}
```

### Package conventions

* Most functions begin with the prefix `drive_`.
* Goal is to allow Drive access that feels similar to Unix file system utilities, e.g. `find`, `ls`, `mv`, `cp`, `mkdir`, and `rm`.
* The metadata for one or more Drive files is held in a `dribble`, a "Drive tibble". This is a data frame with one row per file. A dribble is returned (and accepted) by almost every function in googledrive. It is a compromise between what people want to see (file name), what the API wants (file id), and the metadata needed for general file operations.
* googledrive is "pipe-friendly" and, in fact, re-exports `%>%`, but does not require its use.

### Quick demo

Here's how to list the first 50 files you see in [My Drive](https://drive.google.com). You can expect to be sent to your browser here, to authenticate yourself and authorize the googledrive package to deal on your behalf with Google Drive.

```{r}
drive_find(n_max = 50)
```

You can narrow the query by specifying a `pattern` you'd like to match names against. Or by specifying a file type: the `type` argument understands MIME types, file extensions, and a few human-friendly keywords.

```{r eval = FALSE}
drive_find(pattern = "chicken")
drive_find(type = "spreadsheet")     ## Google Sheets!
drive_find(type = "csv")             ## MIME type = "text/csv"
drive_find(type = "application/pdf") ## MIME type = "application/pdf"
```

Alternatively, you can refine the search using the `q` query parameter. Accepted search clauses can be found in the [Google Drive API documentation](https://developers.google.com/drive/v3/web/search-parameters). For example, to get all files with `'horsebean'` somewhere in their full text (such as files based on the `chickwts` dataset!), do this:

```{r}
(fls <- drive_find(q = "fullText contains 'horsebean'"))
```

You often want to store the result of a googledrive call, as we do with `fls` above. `fls` is a dribble with info on several files and can be used as the input for downstream calls.

#### Identify files

In addition to `drive_find()`, you can also identify files by name (path, really) or by Drive file id using `drive_get()`. `as_id()` can be used to coerce various inputs into a marked vector of file ids. It works on file ids (for obvious reasons!), various forms of Drive URLs, and dribbles.

```{r}
## identify file by path
(x <- drive_get("~/abc/def"))

## let's retrieve it by id (also a great way to force-refresh metadata)
x$id
drive_get(as_id(x$id))
drive_get(as_id(x))
```

In general, googledrive functions that operate on files allow you to specify the file(s) by name/path, file id, or in a `dribble`. If it's ambiguous, use `as_id()` to flag a character vector as holding Drive file ids as opposed to file paths. This function can also extract file ids from various URLs.

#### Upload files

We can upload any file type. 

```{r}
(chicken <- drive_upload(
  drive_example("chicken.csv"),
  "README-chicken.csv"
))
```

Notice that file was uploaded as `text/csv`. Since this was a `.csv` document, and we didn't specify the type, googledrive assumed it was to be uploaded as such (`?drive_upload` for a full list of assumptions). We can overrule this by using the `type` parameter to have it load as a Google Spreadsheet. Let's delete this file first.

```{r}
drive_rm(chicken)

## example of using a dribble as input
chicken_sheet <- drive_upload(
  drive_example("chicken.csv"),
  "README-chicken.csv",
  type = "spreadsheet"
)
```

Much better!

#### Publish files

Versions of Google Documents, Sheets, and Presentations can be published online. You can check your publication status by running `drive_reveal(..., "published")`, which adds a logical column `published` and parks more detailed metadata in a `revision_resource` variable.

```{r}
drive_reveal(chicken_sheet, "published")
```

By default, `drive_publish()` will publish your most recent version.

```{r}
(chicken_sheet <- drive_publish(chicken_sheet))
```

#### Share files

To update the access, we need to change the sharing permissions. Let's say I want anyone with the link to be able to view my dataset.

```{r}
chicken_sheet <- chicken_sheet %>%
  drive_share(role = "reader", type = "anyone")
```

We always assign the return value of googledrive functions back into an R object. This object is of type `dribble`, which holds metadata on one or more Drive files. By constantly re-assigning the value, we keep it current, facilitating all downstream operations.

We can then extract the file's hyperlink.

```{r}
chicken_sheet %>%
  drive_link()
```

#### Download files

##### Google files

We can download files from Google Drive. Native Google file types (such as Google Documents, Google Sheets, Google Slides, etc.) need to be exported to some conventional file type. Specify this explicitly via `type` or implicitly via the file extension in `path`. For example, if I would like to download the "538-star-wars-survey" Google Sheet as a `.csv` I could run the following.

```{r}
drive_download("538-star-wars-survey", type = "csv")
```

Alternatively, I could specify type via the `path` parameter.

```{r}
drive_download(
  "538-star-wars-survey",
  path = "538-star-wars-survey.csv",
  overwrite = TRUE
)
```

Notice in the example above, I specified `overwrite = TRUE`, in order to overwrite the file previously saved.

Finally, you could just allow export to the default type. In the case of Google Sheets, this is an Excel workbook:

```{r}
drive_download("538-star-wars-survey")
```

##### All other files

Downloading files that are *not* Google type files is even simpler, i.e. it does not require any conversion or type info.

```{r}
## upload something we can download
text_file <- drive_upload(drive_example("chicken.txt"), name = "text-file.txt")

## download it and prove we got it
drive_download("text-file.txt")
readLines("text-file.txt") %>% head()
```

#### Clean up

```{r}
drive_rm(chicken_sheet, text_file)
```

```{r, echo = FALSE}
unlink(c(
  "538-star-wars-survey.csv",
  "538-star-wars-survey.xlsx",
  "text-file.txt"
))
```
