---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
## use a token from our development account
## special care with path because wd is docs/ during pkgdown::build_site()
token_path <- rprojroot::find_package_root_file("tidyverse-noncaching-token.rds")
googledrive::drive_auth(token_path)
```

# googledrive

[![Build Status](https://travis-ci.org/tidyverse/googledrive.svg?branch=master)](https://travis-ci.org/tidyverse/googledrive)[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidyverse/googledrive?branch=master&svg=true)](https://ci.appveyor.com/project/tidyverse/googledrive)[![Coverage Status](https://img.shields.io/codecov/c/github/tidyverse/googledrive/master.svg)](https://codecov.io/github/tidyverse/googledrive?branch=master) 

WARNING: this is under very active development

## Overview

`googledrive` interfaces with Google Drive from R, allowing users to seamlessly manage files on Google Drive from the comfort of their console. 

## Installation

```{r, eval = FALSE}
# Obtain the the development version from GitHub:
# install.packages("devtools")
devtools::install_github("tidyverse/googledrive")
```

## Usage

Please see the package website:
<https://tidyverse.github.io/googledrive/>

Here's a teaser that uses googledrive to view the files you see on <https://drive.google.com>:

```{r}
library("googledrive")
drive_find()
```

## Contributing

If you'd like to contribute to the development of googledrive, please read [these guidelines](CONTRIBUTING.md).
