---
title: "publish"
author: "Lucy D’Agostino McGowan"
date: "5/3/2017"
output: 
  github_document:
    toc: true
---
```{r setup, include=FALSE}
library("googledrive")
library("googlesheets")
library("dplyr")
library("readr")
```


## Motivation

Push a table into a Sheet.

Try to read it _as another user_ 
Assume you even have the key.
You will fail.

Now, as the user who owns the Sheet, publish it.

Now, as the other user, try again to read it via googlesheets. You should succeed.


## Push a file into a Sheet
```{r}
drive_auth("drive-token.rds")
file <- drive_upload(
  R.home('doc/BioC_mirrors.csv'),
  type = "spreadsheet"
)
```

## Check publication status (should be FALSE)
```{r}
drive_show_publish(file)
```

## get URL
```{r}
url <- drive_share_link(file)
url
```

## it's published, not shared

```{r}
file
```

```{r}
key <- file$id
```

## switch to different account
```{r, eval = FALSE}
gs_auth("sheets-token.rds")
```


## this shouldn't work
```{r}
try(gs_url(url, visibility = "private", lookup = FALSE))
geterrmessage()
```

## publish it on Drive
```{r}
file <- drive_publish(file)
drive_show_publish(file)
```

## try again!
```{r}
gs_url(url, lookup  = FALSE)
```

check again that the access - it is not shared, but it is published.

```{r}
promote(file, "shared")
```

## clean up

```{r}
drive_rm(file)
```

## Now let's try shared but not published

```{r}
file <- drive_upload(
  R.home('doc/BioC_mirrors.csv'),
  type = "spreadsheet"
)
```

```{r}
file <- drive_share(file, role = "reader", type = "anyone")
```

```{r}
url <- drive_share_link(file)
url
```

## this should work!
```{r}
gs_url(url, visibility = "private", lookup = FALSE)
```

It is not published, but it is shared.

```{r}
file <- drive_show_publish(file)
```

