---
title: "Identifying files on Google Drive"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Identifying files on Google Drive}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
## use a token from our development account
## special care with path because wd is docs/ during pkgdown::build_site()
token_path <- rprojroot::find_package_root_file("tidyverse-noncaching-token.rds")
googledrive::drive_auth(token_path)
```

```{r}
library(googledrive)
```

## `drive_search()` is like My Drive

To see your Google Drive files in the browser, visit <https://drive.google.com>. This displays all your files and offers various ways to filter what you see based on file type, folder, starred vs not, etc.

You can get similar results with `drive_search()`. By default, it gets info on the most recent 100 files.

```{r}
(x <- drive_search())
```

The object you get back holds the metadata for one or more Google Drive files. It is a `dribble`, which is just a `tibble` with Drive files in rows and at least these three variables:

  * `name`: a character vector of file names
  * `id`: a character vector of file ids
  * `files_resource`: a list-column, each element of which holds a list corresponding to a [Files resource](https://developers.google.com/drive/v3/reference/files#resource), which is how the Drive API returns metadata representing a Drive file.
  
There are many ways to filter which files are retrieved, by specifying the `q` query parameter. A few examples:

Just get folders or Google Sheets:

```{r}
## just folders
drive_search(q = "mimeType = 'application/vnd.google-apps.folder'") %>% head(3)

## just Sheets
drive_search(q = "mimeType='application/vnd.google-apps.spreadsheet'") %>% head(3)
```

Files containing `'horsebean'` in their content:

```{r}
drive_search(q = "fullText contains 'horsebean'") %>% head(3)
```

Files in your "Shared with me" collection

```{r}
drive_search(q = "sharedWithMe = true") %>% head(3)
```

googledrive will provide some helpers for [writing these search clauses](https://developers.google.com/drive/v3/web/search-parameters) in due course ([GitHub issue](https://github.com/tidyverse/googledrive/issues/38)).

There is also a `pattern` argument, which will filter the retrieved results for files whose names match a regular expression (which is not supported by the Drive `q` parameter).

```{r}
## this finds nothing because Drive's name search looks only at prefixes
drive_search(q = "name contains 'wts'")

## therefore we do regex matching on the R side
drive_search(pattern = "wts")
```

If you know the exact name, you can use `drive_search()` or, less cumbersome, the `drive_path()` function described next.

```{r}
drive_search(q = "name = '538-star-wars-survey'")
```

## `drive_path()` works on a path

An easier way to get the files that match a name is to use `drive_path()`.

```{r}
drive_path("538-star-wars-survey")
```

Notice that I said "files" with an "s". On Drive, you can have multiple files with the same name, even in the same folder! Furthermore, a file can have multiple parent folders and, therefore, can have more than one path. The functions `drive_path()` and `drive_paths()` operate on one or multiple input paths, respectively, but either of them can return multiple matches per path.

If you want to identify a file by it's name or path, but also make sure that you got a unique match, insert the `confirm_single_file()` utility function in your workflow.

```{r eval = FALSE}
drive_path("538-star-wars-survey") %>% 
  confirm_single_file() %>% 
  drive_browse()
## TO DO: I'd rather put drive_download() here, when it exists
```

To write:

  * the use of `~/`
  * show getting multiple files for one path?
  * show one file can have multiple paths?

## `drive_get()` works on file ids

## `drive_ls()` lists folder contents

