---
title: "Messages and errors in googledrive"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE
)
```

```{r setup}
library(googledrive)
```

*Things I do in a hidden chunk here, to aid exposition about internal tooling:*

* *"Export" the internal helpers covered below*
* *(Attempt to) auth as the service account we use when rendering documentation*
* *Set `.rlang_use_cli_format <- TRUE` in the global workspace, so my `rlang::abort()` calls have the same result as when coming from inside googledrive*

```{r include = FALSE}
drive_bullets <- googledrive:::drive_bullets
bulletize <- googledrive:::bulletize

auth_success <- tryCatch(
  googledrive:::drive_auth_docs(),
  googledrive_auth_internal_error = function(e) e
)

.rlang_use_cli_format <- TRUE
```

## User-facing messages

Everything should be emitted by helpers in `utils-ui.R`, such as `drive_bullets()`.
These helpers are all wrappers around cli functions, such as `cli::cli_bullets()`.

*These may not demo well via pkgdown, but the interactive experience is nice.*

```{r}
drive_bullets(c(
        "noindent",
  " " = "indent",
  "*" = "bullet",
  ">" = "arrow",
  "v" = "success",
  "x" = "danger",
  "!" = "warning",
  "i" = "info"
))
```

The helpers encourage consistent styling and make it possible to selectively silence messages coming from googledrive.
The googledrive message helpers:

-   Use the [cli package](https://cli.r-lib.org/index.html) to get interpolation, inline markup, and pluralization
-   Eventually route through `rlang::inform()`, which is important because `inform()` prints to standard output in interactive sessions. This means that informational messages won't have the same "look" as errors and can generally be more stylish, at least in IDEs like RStudio.
-   Are under the control of the `googledrive_quiet` option. If it's unset, the default is to show messages (unless we're testing, i.e. the environment variable `TESTTHAT` is `"true"`). Doing `options(googledrive_quiet = TRUE)` will suppress messages. There are withr-style convenience helpers: `local_drive_quiet()` and `with_drive_quiet()`.

### Inline styling

How we use the inline classes:

-   `.field` for the value of an argument, e.g. a MIME type
-   `.code` for a column in a data frame and for reserved words, such as
    `NULL`, `TRUE`, and `NA`
-   `.arg`, `.fun`, `.path`, `.cls`, `.url` for their usual purpose

```{r}
drive_bullets(c(
  "We need to talk about the {.arg foofy} argument to {.fun blarg}",
  "You provided {.field a_very_weird_value} and I suspect you're confused \\
   about something"
))
```

Most relevant cli docs:

-   [CLI inline markup](https://cli.r-lib.org/reference/inline-markup.html)
-   [Building a Semantic CLI](https://cli.r-lib.org/articles/semantic-cli.html)

### Bullets

I use the different bullet points in `drive_bullets()` to convey a mood.

Exclamation mark `"!"`: I'm not throwing an error or warning, but I want to get the user's attention, because it seems likely (but not certain) that they misunderstand something about googledrive or Google Drive or their Drive files.
Examples:

```{r}
drive_bullets(c(
  "!" = "Ignoring {.arg type}. Only consulted for native Google file types.",
  " " = "MIME type of {.arg file}: {.field mime_type}."
))

drive_bullets(c(
  "!" = "Currently only fields for the {.field files} resource can be \\
         checked for validity.",
  " " = "Nothing done."
))

drive_bullets(c(
  "!" = "No updates specified."
))

drive_bullets(c(
  "!" = "No such file to delete."
))
```

Information "i": I'm just keeping you informed of how my work is going.

```{r}
drive_bullets(c(
  "i" = "No pre-existing file at this filepath. Calling \\
         {.fun drive_upload}."
))

drive_bullets(c(
  "i" = "Pre-existing file at this filepath. Calling \\
         {.fun drive_update}."
))

drive_bullets(c(
  "i" = "Not logged in as any specific Google user."
))
```

In cases where we determine there is nothing we can or should do, sometimes I use `"!"` and sometimes I use `"i"`.
It depends on whether it feels like the user could or should have known that no work would be possible or needed.

### Programmatic generation of bullets

Often we need to create bullets from an R object, such as a character vector or a dribble.
What needs to happen:

* Map a cli-using string template over the object to get a character vector
* Truncate this vector in an aesthetically pleasing way
* Apply names to this vector to get the desired bullet points

`map_cli()` is an internal generic that turns an object into a vector of strings with cli markup.
Currently `map_cli()` has methods for `character` and `dribble` (and `NULL` and a `default`).

```{r}
map_cli(letters[1:3])
```

By default `map_cli.character()` just applies the `.field` style, i.e. the template is `"{.field <<x>>}"`.
But the template can be customized, if you need something else.
Note that we use non-standard glue delimiters (`<<` and `>>`, by default), because we are interpolating into a string with glue/cli markup, where `{}` has the usual meaning.

```{r}
map_cli(letters[4:6], template = "how about a path {.path <<x>>}?")
```

The `map_cli.dribble()` method makes a cli-marked up string for each row of the dribble, i.e. for each Drive file.

```{r}
dat <- drive_find(n_max = 5)
map_cli(dat)
```

`map_cli.dribble()` also allows a custom template, but it's a more complicated and less common situation than for `character`.
We won't get into that here.
(I don't consider the dribble styling to be finalized yet.)

The result of `map_cli()` then gets processed with `bulletize()`, which adds the bullet-specifying names and does aesthetically pleasing truncation.

```{r}
bulletize(map_cli(letters))

bulletize(map_cli(letters), bullet = "x", n_show = 2)

drive_bullets(c(
  "These are surprising things:",
  bulletize(map_cli(letters), bullet = "!")
))

dat <- drive_find(n_max = 10)

drive_bullets(c(
  "Some Drive files:",
  bulletize(map_cli(dat))
))
```

## Errors

I am currently trying out <https://github.com/r-lib/rlang/pull/1176>, which means messages from `rlang::abort()` and `rlang::warn()` are processed via cli, just like those sent through `drive_bullets()`.

Here are some current points of friction.

### Who's in charge?

This feels weird and asymmetrical:

* If I want to throw an error, I call `rlang::abort()` (directly) and turn on
  cli support by assigning `.rlang_use_cli_format <- TRUE` in my namespace.
* If I want to emit an informational message, I call `cli::cli_bullets()`
  (indirectly, because I need to tweak theme and respect package verbosity),
  which sends the message through `rlang::inform()` for me.

It's great that rlang and cli are working together to provide the UI.
It just feels odd that I regard rlang as primary for errors (and warnings) and cli as primary for informational messages.

### Theme tweaking

I think it is inevitable that packages will need to tweak or add to the current cli theme.

Examples:

* I like to have a "quote if no color" fallback for, e.g., the `.field` style.
* You might map an existing style to a domain-relevant term.
* I'm considering making regular `"*"` bullets un-colored, because I might use
  color in, e.g., Drive file formatting and I don't want too much color.
  
The obvious place to enact these tweaks is in the `drive_bullets()` wrapper I have around `cli::cli_bullets()`.
This wrapper seems almost unavoidable, if I want to have package-specific verbosity control.

But where do I put these tweaks so that they also affect `abort()`?
This suggests the creation of another wrapper around `abort()`, but this is exactly what we are hoping to avoid.

Notice how the letters are single-quoted when emitted by `drive_bullets()`, which is equipped with "quote if not color" behaviour, but are not when emitted by `abort()`.

```{r}
withr::with_envvar(
  c("NO_COLOR" = 1),
  {
    drive_bullets(c(
      "I want to chat about these fields:",
      bulletize(map_cli(letters[1:3]))
    ))
    
    # remember I did this hack:
    # .rlang_use_cli_format <- TRUE, in global env, in hidden setup chunk
    rlang::abort(c(
      "I cannot work with these fields:",
      bulletize(map_cli(letters[1:3]))
    ))    
  }
)
```

It feels like the solution to this could be related to the solution of the previous point, with some richer package-level configuration for the combined use of rlang and cli.

### Hard-to-reach switch

In this document, it's hard to demo the difference between `drive_bullets()` and what `rlang::abort()` does *when called from googledrive*, because the switch to turn on cli-formatting is so tied to package namespace.
The current hack is I define `.rlang_use_cli_format <- TRUE` in a hidden chunk.

Is that the preferred long-term solution, when someone needs to do a small demo of rlang with cli switched on?

### Message truncation

`abort()` messages appear to get truncated.
If you're inserting programmatically generated bullet points, this can mean an important part of the overall message is not actually presented to the user.

Here I present a bulletized dribble via `abort()` and `drive_bullets()` (wrapper around `cli::cli_bullets()`).
Note that we see message header, bullets, and conclusion.

```{r}
dat <- drive_find()
dat <- rbind(dat, dat, dat)

rlang::abort(c(
  "Uh-oh, something is wrong with these Drive files:",
  bulletize(map_cli(dat)),
  "i" = "Advice on how to fix this"
))

drive_bullets(c(
  "Yo, I have something to say about these Drive files:",
  bulletize(map_cli(dat)),
  "i" = "Advice on how to fix this"
))
```

But what if I reveal info on more Drive files, instead of 5?
The `abort()` message gets truncated.
At least, it does in the Console.
Maybe when rendering `.Rmd`, it does not?
Interactively, I've even seen it truncate in the middle of a bullet point.

```{r}
rlang::abort(c(
  "Uh-oh, something is wrong with these Drive files:",
  bulletize(map_cli(dat), n_show = 20),
  "i" = "Advice on how to fix this"
))

drive_bullets(c(
  "Yo, I have something to say about these Drive files:",
  bulletize(map_cli(dat), n_show = 20),
  "i" = "Advice on how to fix this"
))
```

### Message wrapping

`abort()` sometimes wraps to a different width.
I've seen this several times, but I can't reproduce it now.
But somehow, it seems you can get into a state where `abort()` isn't wrapping to the same width as cli.
