---
title: "Dealing with multiple files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dealing with multiple files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
## use a token from our development account
token_path <- rprojroot::find_package_root_file("tidyverse-noncaching-token.rds")
googledrive::drive_auth(token_path)
```

Some googledrive functions are built to naturally handle multiple files, while others operate on a single file.

Functions that expect a single file:

* `drive_browse()`  
* `drive_cp()`  
* `drive_download()` 
* `drive_ls()`
* `drive_mkdir()`
* `drive_mv()`  
* `drive_rename()`  
* `drive_update()`
* `drive_upload()`

Functions that allow multiple files: 

* `drive_publish()`  
* `drive_reveal()`  
* `drive_rm()`  
* `drive_share()`  
* `drive_trash()`  

In general, the principle is: if there are multiple parameters that are likely to vary across multiple files, the function is designed to take a single input. In order to use these function with multiple inputs, use them together with your favorite approach for iteration in R. Below is a worked example, focusing on tools in the tidyverse, namely the `map()` functions in purrr.

## Upload multiple files, then rename them

Scenario: we have multiple local files we want to upload into a folder on Drive. Then we regret their original names and want to rename them.

Load packages.

```{r}
library(googledrive)
library(glue)
library(tidyverse)
```

### Upload

Use the example files that ship with googledrive. This looks a bit odd, but the first call returns their names and the second returns full paths on the local system.

```{r}
local_files <- drive_example() %>% 
  drive_example()
```

Create a folder on your Drive and upload all files into this folder by iterating over the `local_files` using `purrr::map()`.

```{r}
folder <- drive_mkdir("upload-into-me-article-demo")
files <- map(local_files, drive_upload, path = folder, verbose = FALSE)
```

`files` is now a list of **dribbles**, one per uploaded file. Let's confirm that we uploaded the file into the new folder.

```{r}
str(files, max.level = 1)
drive_ls(folder)
```

### Rename

Imagine that we now wish these file names had a date prefix. First, form the new names. We use `glue::glue()` for string interpolation but you could also use `paste()`. Second, we map over two inputs: the list of dribbles from above and the vector of new names.

```{r}
new_names <- glue("{Sys.Date()}_{basename(local_files)}")
files_dribble <- map2_df(files, new_names, drive_rename)
## alternative: do this to get a list of dribbles for more downstream mapping
# files_list <- map2(files, new_names, drive_rename)
```

We use `purrr::map2_df()` to work through the list of dribbles (= Drive files) and the vector of new names and row bind the returned dribbles into a single dribble holding all files. In commented out code, we show an alternative using `purrr::map2()` that would return another list of dribbles. This would set you up better for downstream operations that required more `map()`ing.

Let's check on the contents of this folder again:

```{r}
drive_ls(folder)
```

Note that you can always row bind individual dribbles into one big dribble yourself. We demo that with `dplyr::bind_rows()`:

```{r}
bind_rows(files)
```

### Clean up

Our trashing function, `drive_trash()` is vectorized and can therefore operate on a multi-file dribble. We could trash these files like so:

```{r eval = FALSE}
drive_trash(files_dribble)
```

If you're absolutely sure of yourself and happy to do something irreversible, you could truly delete these files with `drive_rm()`, which is also vectorized:

```{r eval = FALSE}
drive_rm(files_dribble)
```

Finally -- and this is the code we will actually execute -- the easiest way to delete these files is to delete their enclosing folder.

```{r}
drive_rm(folder)
```
