---
title: "Dealing with multiple files"
---

```{r setup, include = FALSE}
auth_success <- tryCatch(
  googledrive:::drive_auth_docs(),
  googledrive_auth_internal_error = function(e) e
)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE,
  purl = googledrive::drive_has_token(),
  eval = googledrive::drive_has_token()
)

options(tidyverse.quiet = TRUE)
```

```{r eval = !googledrive::drive_has_token(), echo = FALSE, comment = NA}
googledrive:::drive_bullets(c(
  "Code chunks will not be evaluated, because:",
  strsplit(auth_success$message, split = "\n")[[1]]
))
googledrive::drive_deauth()
```

```{r, include = FALSE}
# clean up if any previous runs left this lying around
trash_me <- googledrive::drive_find(
  "upload-into-me-article-demo", type = "folder"
)
if (googledrive::some_files(trash_me)) {
  googledrive::drive_trash(trash_me)
}
```

Some googledrive functions are built to naturally handle multiple files, while others operate on a single file.

Functions that expect a single file:

* `drive_browse()`  
* `drive_cp()`  
* `drive_download()` 
* `drive_ls()`
* `drive_mv()`  
* `drive_put()`
* `drive_rename()`  
* `drive_update()`
* `drive_upload()`

Functions that allow multiple files: 

* `drive_publish()`  
* `drive_reveal()`  
* `drive_rm()`  
* `drive_share()`  
* `drive_trash()`  

In general, the principle is: if there are multiple parameters that are likely to vary across multiple files, the function is designed to take a single input. In order to use these function with multiple inputs, use them together with your favorite approach for iteration in R. Below is a worked example, focusing on tools in the tidyverse, namely the `map()` functions in purrr.

## Upload multiple files, then rename them

Scenario: we have multiple local files we want to upload into a folder on Drive. Then we regret their original names and want to rename them.

Load packages.

```{r}
library(googledrive)
library(glue)
library(tidyverse)
```

### Upload

Use the example files that ship with googledrive.

```{r}
local_files <- drive_examples_local()
local_files <- set_names(local_files, basename(local_files))
local_files
```

Create a folder on your Drive and upload all files into this folder by iterating over the `local_files` using `purrr::map()`.

```{r}
folder <- drive_mkdir("upload-into-me-article-demo")
with_drive_quiet(
  files <- map(local_files, ~ drive_upload(.x, path = folder))
)
```

First, let's confirm that we uploaded the files into the new folder.

```{r}
drive_ls(folder)
```

Now let's reflect on the `files` object returned by this operation. `files` is a list of **dribbles**, one per uploaded file.

```{r}
str(files, max.level = 1)
```

This would be a favorable data structure if you've got more `map()`ing to do, as you'll see below.

But what if not? You can always row bind individual dribbles into one big dribble yourself with, e.g., `dplyr::bind_rows()`.

```{r}
bind_rows(files)
```

Below we show another way to finesse this by using a variant of `purrr::map()` that does this for us, namely `map_dfr()`.

### Rename

Imagine that we now wish these file names had a date prefix. First, form the new names. We use `glue::glue()` for string interpolation but you could also use `paste()`. Second, we map over two inputs: the list of dribbles from above and the vector of new names.

```{r}
(new_names <- glue("{Sys.Date()}_{basename(local_files)}"))
files_dribble <- map2_dfr(files, new_names, drive_rename)
```

We use `purrr::map2_dfr()` to work through `files`, the list of dribbles (= Drive files), and `new_names`, the vector of new names, and row bind the returned dribbles into a single dribble holding all files.

Let's check on the contents of this folder again to confirm the new names:

```{r}
drive_ls(folder)
```

Let's confirm that, by using `map2_df2()` instead of `map2()`, we got a single dribble back, instead of a list of one-row dribbles:

```{r}
files_dribble
```

What if you wanted to get a list back, because your downstream operations include yet more `map()`ing? Then you would use `map2()`.

```{r eval = FALSE}
files_list <- map2(files, new_names, drive_rename)
```

### Clean up

Our trashing function, `drive_trash()` is vectorized and can therefore operate on a multi-file dribble. We could trash these files like so:

```{r eval = FALSE}
drive_trash(files_dribble)
```

If you're absolutely sure of yourself and happy to do something irreversible, you could truly delete these files with `drive_rm()`, which is also vectorized:

```{r eval = FALSE}
drive_rm(files_dribble)
```

Finally -- and this is the code we will actually execute -- the easiest way to delete these files is to delete their enclosing folder.

```{r}
drive_rm(folder)
```
