---
title: "File permissions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Dealing with permissions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
## use a token from our development account
token_path <- rprojroot::find_package_root_file("tidyverse-noncaching-token.rds")
googledrive::drive_auth(token_path)
```

You can use googledrive to manage permissions on your Drive files, i.e. grant different people or groups of people various levels of access (read, comment, edit, etc.).

Let's upload a file and view its permissions.

```{r}
library(googledrive)
file <- drive_example("chicken.txt") %>%
  drive_upload(name = "chicken-perm-article.txt") %>% 
  drive_reveal("permissions")
file
```

The `shared` column shows that this file is not yet shared with anyone and, for those so inclined, detailed information on permissions can be found in the `permissions_resource` list-column.

Let's give a specific person permission to edit this file and a customized message, using the `emailAddress` and `emailMessage` parameters.

```{r, eval = FALSE}
file <- file %>%
  drive_share(
    role = "writer",
    type = "user",
    emailAddress = "serena@example.com",
    emailMessage = "Would appreciate your feedback on this!"
  )
file
```

```{r, echo = FALSE}
file <- file %>%
  drive_share(
    role = "writer",
    type = "user",
    emailAddress = "jenny@stat.ubc.ca",
    emailMessage = "Would appreciate your feedback on this!"
  )
file
```

We see that the file is now shared. We also want anyone to be able to read the file.

```{r}
file <- file %>%
  drive_share(role = "reader", type = "anyone")
```

Now that we've made a few updates to our permissions, the `permissions_resource` list-column has become more interesting. Here's how to pull important information out of this and put into a tibble with one row per permission. (*Permission handling will become more formalized in future versions of googledrive. See [the issue](https://github.com/tidyverse/googledrive/issues/180)*). We use other packages in the tidyverse now for this data wrangling.

```{r}
library(tidyverse)
perm <- pluck(file, "permissions_resource", 1, "permissions")
permissions <- tibble(
  id = map_chr(perm, "id", .null = NA_character_),
  name = map_chr(perm, "displayName", .null = NA_character_),
  type = map_chr(perm, "type", .null = NA_character_),
  role = map_chr(perm, "role", .null = NA_character_),
  email = map_chr(perm, "emailAddress", .null = NA_character_)
)
as.data.frame(permissions)
```

## Clean up

```{r}
drive_rm(file)
```


