---
title: "File permissions"
---

```{r setup, include = FALSE}
auth_success <- tryCatch(
  googledrive:::drive_auth_docs(),
  googledrive_auth_internal_error = function(e) e
)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  error = TRUE,
  purl = googledrive::drive_has_token(),
  eval = googledrive::drive_has_token()
)

options(tidyverse.quiet = TRUE)
```

```{r eval = !googledrive::drive_has_token(), echo = FALSE, comment = NA}
googledrive:::drive_bullets(c(
  "Code chunks will not be evaluated, because:",
  strsplit(auth_success$message, split = "\n")[[1]]
))
googledrive::drive_deauth()
```

```{r, include = FALSE}
# clean up if any previous runs left this lying around
trash_me <- googledrive::drive_find("chicken-perm-article")
if (googledrive::some_files(trash_me)) {
  drive_trash(trash_me)
}
```

You can use googledrive to manage permissions on your Drive files, i.e. grant different people or groups of people various levels of access (read, comment, edit, etc.).

Let's upload a file and view its permissions.

```{r}
library(googledrive)

file <- drive_example_local("chicken.txt") %>%
  drive_upload(name = "chicken-perm-article.txt") %>% 
  drive_reveal("permissions")

file
```

`shared = FALSE` indicates that this file is not yet shared with anyone and, for those so inclined, detailed information on permissions can be found in the `permissions_resource` list-column. Note that the `drive_resource`, which is always present in a dribble, typically also contains information on permissions. So if you just want to *know* about permissions, as opposed to modifying them, you can probably consult `drive_resource`.

Let's give a specific person permission to edit this file and a customized message, using the `emailAddress` and `emailMessage` parameters.

```{r, eval = FALSE}
file <- file %>%
  drive_share(
    role = "writer",
    type = "user",
    emailAddress = "serena@example.com",
    emailMessage = "Would appreciate your feedback on this!"
  )
```

Let's say we also want "anyone with a link" to be able to read the file.

```{r eval = FALSE}
file <- file %>%
  drive_share(role = "reader", type = "anyone")
```

This comes up often enough that we've made a convenience wrapper:

```{r}
file <- file %>%
  drive_share_anyone()
file
```

We see that the file is now `shared = TRUE`.

Now that we've made a few updates to our permissions, the `permissions_resource` list-column has become more interesting. Here's how to pull important information out of this and put into a tibble with one row per permission. (*Permission handling will become more formalized in future versions of googledrive. See [the issue](https://github.com/tidyverse/googledrive/issues/180)*). We use other packages in the tidyverse now for this data wrangling.

```{r eval = FALSE}
library(tidyverse)

perm <- pluck(file, "permissions_resource", 1, "permissions")

permissions <- tibble(
  id =    map_chr(perm, "id",           .default = NA_character_),
  name =  map_chr(perm, "displayName",  .default = NA_character_),
  type =  map_chr(perm, "type",         .default = NA_character_),
  role =  map_chr(perm, "role",         .default = NA_character_),
  email = map_chr(perm, "emailAddress", .default = NA_character_)
)
permissions
```

We've suppressed execution of the above chunk but here's some static, indicative output:

```{r eval = FALSE}
#> # A tibble: 3 x 5
#>   id           name            type   role  email                      
#>   <chr>        <chr>           <chr>  <chr> <chr>                      
#> 1 12345678901… Serena Somebody user   writ… serena@example.com          
#> 2 anyoneWithL… NA              anyone read… NA                         
#> 3 98765432109… Orville Owner   user   owner orville@example.com
```

## Clean up

```{r}
drive_rm(file)
```
