---
title: "big picture"
author: "Lucy D’Agostino McGowan"
date: "4/26/2017"
output: 
  github_document:
    toc: true
---

*side note, really excited to include emojis in a non-hacky way, thanks [emo::ji](http://github.com/hadley/emo)* `r emo::ji("sunflower")`

```{r, message = FALSE, warning = FALSE}
library('googledrive')
library('dplyr')
drive_auth("drive-token.rds")
```

## List

`drive_list()` pulls out name, type, & id 

```{r}
drive_list()
```

We can search using regular expressions

```{r}
drive_list(pattern = "test")
```

We can also pass additional query parameters through the `...`, for example

```{r}
drive_list(pattern = "test", orderBy = "modifiedTime")
```

## Metadata

Note: now it seems we have to specify the fields (in v2 where I was working previously, it would automatically output everything, see [this](https://developers.google.com/drive/v3/web/migration)).

List of all fields [here](https://developers.google.com/drive/v3/web/migration).

Now let's say I want to dive deeper into the top one

```{r}
id <- drive_list("test")$id[1]
file <- drive_file(id)
file
```

In addition to the things I've pulled out, there is a `tibble` of permissions as well as a  `list` (now named `kitchen_sink`, this should change), that contains all output fields.

```{r}
file$permissions
```


```{r}
str(file$kitchen_sink)
```


## User info

```{r}
drive_user()
```

## Upload file

```{r}
write.table("this is a test", file = "~/desktop/test.txt")
drive_upload(input = "~/desktop/test.txt", output = "This is a test", overwrite = TRUE)
```

```{r}
file <- drive_file(drive_list("This is a test")$id)
file
```

## Update sharing

```{r}
file <- drive_share(file, role = "writer", type = "user", emailAddress = "dagostino.mcgowan.stats@gmail.com",emailMessage = "I am sharing this cool file with you. Now you can write. You are welcome." )
```

## View permissions

```{r}
file$permissions %>%
  select(displayName,role, type)
```

## Make it fully shareable

```{r}
file <- drive_share(file, role = "reader", type = "anyone", allowFileDiscovery = "true")
```

## Extract share link
```{r}
drive_share_link(file)
```

*this looks exactly the same as the share link from the Google Drive GUI except `usp=drivesdk` instead of `usp=sharing`*

## Delete file
```{r}
drive_delete(file)
```



