---
title: "playing"
author: "Lucy D’Agostino McGowan"
date: "4/26/2017"
output: 
  github_document:
    toc: true
---

*side note, really excited to include emojis in a non-hacky way, thanks [emo::ji](http://github.com/hadley/emo)* `r emo::ji("sunflower")`

```{r, message = FALSE, warning = FALSE}
library('googledrive')
library('dplyr')
```

this is almost an exact copy of how `gs_auth()` works
```{r}
gd_auth() 
```

## List

`gd_ls()` pulls out name, type, & id 
(we probably don't want to see id, but seems useful to have here, so we could pick which one we want to get more info on?)
```{r}
gd_ls()
```

## Metadata

Note: now it seems we have to specify the fields (in v2 where I was working previously, it would automatically output everything, see [this](https://developers.google.com/drive/v3/web/migration)).

List of all fields [here](https://developers.google.com/drive/v3/web/migration).

Now let's say I want to dive deeper into the top one

```{r}
metadata_tbl <- gd_ls() %>%
                  slice(1) %>%
                  select(id) %>%
                  gd_get()
metadata_tbl
```

It looks a bit repetitive - right now I have a separate line for everyone permission

```{r}
metadata_tbl %>%
  select(name, permission_who, permission_role)
```

In addition to the things I've pulled out, there is a `list-col` (now named `object`, this should change), that contains all output fields.

```{r}
metadata_tbl %>%
  select(object)
```

## User info

```{r}
gd_user()
```

