---
title: "sharing demo"
author: "Lucy D’Agostino McGowan"
date: "5/3/2017"
output: 
  github_document:
    toc: true
---

This is a little demo to show how we may view sharing.

```{r, message = FALSE, warning = FALSE}
library('dplyr')
library('googledrive')
```

```{r}
write.table("Sharing demo", "sharing_demo.txt")
gd_upload("sharing_demo.txt")
```

```{r}
my_file <- gd_get_id("sharing_demo") %>%
  gd_file()
```

## check current permissions
```{r}
my_file$permissions
```

cool beans - it's private!

## change permissions (anyone with link)

```{r}
my_file %>%
  gd_share(role = "reader", type = "anyone")
```

Let's see what that did

```{r}
my_file <- gd_get_id("sharing_demo") %>%
  gd_file()

my_file$permissions
```

Now anyone with the link can view it

## change permissions (anyone in the `r emo::ji('world')`)

```{r}
my_file %>%
  gd_share(role = "reader", type = "anyone", allowFileDiscovery = "true")
```

Let's see what that did

```{r}
my_file <- gd_get_id("sharing_demo") %>%
  gd_file()

my_file$permissions
```

## make it easier to see

I've added `access` to the Google Drive file object
```{r}
my_file$access
```

and also to the print method:

```{r}
my_file
```

## clean up

```{r}
gd_delete(my_file)
```

