---
title: "sharing demo"
author: "Lucy D’Agostino McGowan"
date: "5/3/2017"
output: 
  github_document:
    toc: true
---

This is a little demo to show how we may view sharing.

```{r, message = FALSE, warning = FALSE}
library('dplyr')
library('googledrive')
drive_auth("drive-token.rds")
```

```{r}
write.table("This is a little demo", "demo.txt")
drive_upload("demo.txt", "Happy Little Demo")
```

```{r}
my_file <- drive_list("Happy Little Demo")$id %>%
  drive_file()
```

## check current permissions
```{r}
my_file
```

cool beans - it's private!

## change permissions (anyone with link)

*all functions that will somehow change the file will output a new file, overwrite the old file with this to avoid confusion*
```{r}
my_file<- my_file %>%
  drive_share(role = "reader", type = "anyone")
```

Let's see what that did

```{r}
my_file
```

Now anyone with the link can view it

## change permissions (anyone in the `r emo::ji('world')`)

```{r}
my_file <- my_file %>%
  drive_share(role = "reader", type = "anyone", allowFileDiscovery = "true")
```

Let's see what that did

```{r}
my_file
```

## make it easier to see

I've added `access` to the Google Drive file object
```{r}
my_file$access
```

## share link

you can also output a link to share
```{r}
drive_share_link(my_file)
```

## clean up

```{r}
drive_delete(my_file)
```

```{r, echo = FALSE}
rm <- file.remove("demo.txt")
```

