---
title: "passing queries in the dots!"
author: "Lucy D’Agostino McGowan"
date: "5/9/2017"
output: 
  github_document:
    toc: true
---

*This is all about those dots[.](https://www.youtube.com/watch?v=GI6CfKcMhjY)*

Most of the functions have `...` which allow the user to input name-value pairs to query the API.

```{r, message = FALSE, warning = FALSE}
library('googledrive')
library('dplyr')
```

## List files

We list files using `gd_ls()`[.](https://www.youtube.com/watch?v=F-X4SLhorvw) Possible parameters to pass to the `...` can be found here. For example, by default files are listed in descending order by most recently modified.  

Here is my list using the default:

```{r}
gd_ls()
```

Let's say I want to order them by folders, then modified time, then name. I can do that!

```{r}
gd_ls(orderBy = "folder,modifiedTime desc,name" )
```

As another example, by default, this will list 100 drive files. If we want to output more, we can pass the `pageSize` parameter[.](https://www.youtube.com/watch?v=cRpdIrq7Rbo&t=67s)

```{r}
gd_ls(pageSize = 200)
```

## Publish files

To publish files, we use `gd_publish()`. Parameters found [here](https://developers.google.com/drive/v3/reference/revisions/update) can be passed to the `...` of this function. For example, by default for Google Docs, subsequent revisions will be automatically republished. We can change this by passing the `publishAuto` parameter.

```{r}
my_file <- gd_get_id("test") %>%
  gd_file %>%
  gd_publish(publishAuto=FALSE)
```

```{r}
my_file$publish
```

## Share files

To share files, we use `gd_share()`. Parameters that can be passed to the `...` can be found [here](https://developers.google.com/drive/v3/reference/permissions/create). For example, if we set the `type` parameter as `anyone`, we can pass the `allowFileDiscovery` through the `...` to allow anyone to discover the file (this is equivalent to being "Public on the Web").

```{r}
my_file <- my_file %>%
  gd_share(type = "anyone", role = "writer", allowFileDiscovery = TRUE)
```

```{r}
my_file$permissions
```

I also display this in the print method.

```{r}
my_file
```

## Uploading a file

To upload a file we use `gd_upload()`. Parameters that can be passed to the `...` can be found [here](https://developers.google.com/drive/v3/reference/files/update). For example, if you would like to add a file to a specific folder, and do not want to use the `gd_mv` function after, you can use `addParents`.

Let's grab a folder to stick the file in.
```{r}
folder <- gd_get_id("THIS IS A TEST") %>%
  gd_file
```


Make sure it's a folder.
```{r}
folder
```

Upload to the folder.
```{r}
new_file <- gd_upload("demo.txt",addParents = folder$id)
```


## clean up
```{r}
new_file <- gd_delete(new_file)
```

