---
title: "Playing with `drive_upload()`"
author: "Lucy D’Agostino McGowan"
date: "7/14/2017"
output: github_document
---

```{r}
library("googledrive")
library("testthat")
```

Let's upload a file.

```{r}
drive_auth("drive-token.rds")
x <- drive_upload(system.file("DESCRIPTION"), "test-upload-lucy")
```

## overwrite using a `dribble`

Let's try to upload a file into that same location, using the `x` dribble object.
```{r}
## this should error
expect_error(y <- drive_upload(system.file("DESCRIPTION"), x),
             "File already exists"
)
```

Let's add set the parameter `overwrite = TRUE`. Now this should work.
```{r}
y <- drive_upload(system.file("DESCRIPTION"), x, overwrite = TRUE)
```

The `id`s for `x` and `y` should be identical. 
```{r}
expect_identical(y$id, x$id)
```

## overwrite using a `name`

```{r}
y <- drive_upload(system.file("DESCRIPTION"), "test-upload-lucy", overwrite = TRUE)
```

```{r}
expect_identical(y$id, x$id)
```

If we do not set the parameter `overwrite = TRUE`, it should still create the file. Now we will have 2 files in the same location with the same name.

```{r}
y <- drive_upload(system.file("DESCRIPTION"), "test-upload-lucy")
```

Now the `id`s should no longer be identical.
```{r}
expect_false(x$id == y$id)
```

```{r}
drive_find("test-upload-lucy")
```

If we try to overwrite *again*, we should receive an error, since we don't know which to overwrite.

```{r}
expect_error(
  z <- drive_upload(system.file("DESCRIPTION"),
                    "test-upload-lucy",
                    overwrite = TRUE),
  "Path to overwrite is not unique"
)
```

If we use the `x` or `y` `dribble`, however, we should still be able to overwrite.

```{r}
z <- drive_upload(system.file("DESCRIPTION"), x, overwrite = TRUE)
```

```{r}
expect_equal(z$id, x$id)
```

## folders

Let's make sure this plays nice with folders
```{r}
folder <- drive_mkdir("test-folder-lucy")
```

```{r}
a <- drive_upload(system.file("DESCRIPTION"), folder, "test-upload-lucy")
```
Let's make sure `a` is actually in `folder`.
```{r}
a_parent <- unlist(a$files_resource[[1]]$parents)
expect_equal(a_parent, folder$id)
```

```{r}
b <- drive_upload(system.file("DESCRIPTION"), a, overwrite = TRUE)
```

`b` should also exist in `folder`.

```{r}
b_parent <- unlist(b$files_resource[[1]]$parents)
expect_equal(b_parent, folder$id)
```

If I try to give it a new name, it should error.
```{r}
expect_error(
  c <- drive_upload(system.file("DESCRIPTION"), b, name = "new_name", overwrite = TRUE),
  "Requested parent folder does not exist"
)
```
*hmm is this a sensible error? it definitely makes sense in some circumstances but...*

Note: *if you want to overwrite AND give it a new name, you have to use `drive_rename()`.

## clean up

```{r}
drive_rm("test-upload-lucy")
```

