---
title: "Playing with `drive_upload()`"
author: "Lucy D’Agostino McGowan"
date: "7/14/2017"
output: github_document
---

```{r}
library("googledrive")
library("testthat")
```

Let's upload a file.

```{r}
drive_auth("drive-token.rds")
x <- drive_upload(system.file("DESCRIPTION"), "test-upload-lucy")
```

## overwrite using a `dribble`

Let's try to upload a file into that same location, using the `x` dribble object.
```{r, error = TRUE}
## this should error
y <- drive_upload(system.file("DESCRIPTION"), x)
```

Let's add set the parameter `overwrite = TRUE`. Now this should work.
```{r}
y <- drive_upload(system.file("DESCRIPTION"), x, overwrite = TRUE)
```

The `id`s for `x` and `y` should be identical. 
```{r}
identical(y$id, x$id)
```

## overwrite using a character `path`

```{r}
y <- drive_upload(system.file("DESCRIPTION"), "test-upload-lucy", overwrite = TRUE)
```

```{r}
identical(y$id, x$id)
```

If we do not set the parameter `overwrite = TRUE`, it should still create the file when `path` is character. Now we will have 2 files in the same location with the same name.

```{r}
y <- drive_upload(system.file("DESCRIPTION"), "test-upload-lucy")
```

Now the `id`s should no longer be identical.
```{r}
!identical(x$id, y$id)
```

```{r}
drive_find("test-upload-lucy")
```

If we try to overwrite *again*, we should receive an error, since we don't know which to overwrite.

```{r, error = TRUE}
z <- drive_upload(system.file("DESCRIPTION"),
                  "test-upload-lucy",
                  overwrite = TRUE)
```

If we specify the `x` or `y` `dribble` as the `path`, however, we should still be able to overwrite.

```{r}
z <- drive_upload(system.file("DESCRIPTION"), x, overwrite = TRUE)
```

```{r}
identical(z$id, x$id)
```

If we specify the `x` `dribble` as a `path`, AND specify a `name`, it will error that `x` is not a folder. If you specify BOTH a `path` and a `name`, the expectation is that the `path` is intended to be a folder. 

You will receive the following error if you give a `name` AND you give something in `path` that DOES exist on your Drive, but that is NOT a folder.

```{r, error = TRUE}
z <- drive_upload(system.file("DESCRIPTION"), x, name = "new name", overwrite = TRUE)
```

## folders

Let's make sure this plays nice with folders
```{r}
folder <- drive_mkdir("test-folder-lucy")
```

```{r}
a <- drive_upload(system.file("DESCRIPTION"), folder, "test-upload-lucy")
```

Let's make sure `a` is actually in `folder`.
```{r}
a_parent <- unlist(a$files_resource[[1]]$parents)
identical(a_parent, folder$id)
```

```{r}
b <- drive_upload(system.file("DESCRIPTION"), a, overwrite = TRUE)
```

`b` should also exist in `folder`.

```{r}
b_parent <- unlist(b$files_resource[[1]]$parents)
identical(b_parent, folder$id)
```

If I try to give it a new name, it should be okay now, since `folder` is a valid folder.
```{r}
c <- drive_upload(system.file("DESCRIPTION"), folder, name = "new_name", overwrite = TRUE)
```

If I try to stick it in a folder that does not exist, it should complain that the path is not on Drive. You will receive this error if you give any `path` but it does not exist on your Drive.
```{r, error = TRUE}
c <- drive_upload(system.file("DESCRIPTION"), "this is not a real folder", name = "new_name", overwrite = TRUE)
```

Note: *if you want to overwrite AND give it a new name, you have to use* `drive_rename()`.


## clean up

```{r}
drive_rm(c("test-upload-lucy", "test-folder-lucy"))
```

